Classless Java: Tuning Java Interfaces

### 2016-03-04 OOPSLA16/sections/Translation.tex
more functions in main body

@@

@@

Figure~\ref{figure:translation} presents the translation functions. In the first function, $\mixinAnn$
injects refined methods to interface $\C_0$, while in the second function, $\weakAnn$ invokes 
$\ofMethod(\C_0)$ and generates the $\QM{of}$
method for $\C_0$, if such a method does not exist in its domain, and all the abstract methods are
valid for the annotation. The formal definition is available in Appendix~\ref{subsec:translation}.

>>>>

\begin{figure*}[t]\label{figure:valid}
\centering
\hspace{-.3in}
\begin{minipage}[b]{0.5\textwidth}
$\begin{array}{l}
\InTextDef{16em}{\C_0\ \QM{with#}\m\oR \C\ \QM{_val}\cR\QM;\in
\otherMethod(\C_0,\methods)}{}\\
\hspace{.25in}\isWith(\mBody(\QM{with#}\m, \C_0), \C_0),\
\QM{with#}\m\notin\dom(\methods)\\
\InTextDef{16em}{\C_0\ \QM_\m\oR \C\ \QM{_val}\cR\QM;\in
\otherMethod(\C_0,\methods)}{}\\
\hspace{.25in}\isSetter(\mBody(\QM_\m, \C_0), \C_0),\ \QM_\m\notin\dom(\methods)\\
\InTextDef{7ex}{\valid(\C_0)}{\forall \m\in\dom(\C_0),\mbox{ if }\mh\QM; =
            \mBody(\m, \C_0),}\\
            \hspace{.24in}\mbox{ one of the following cases is satisfied:}\\
\tab\tab
\isField(\method), \isWith(\method, \C_0) \mbox{ or }
\isSetter(\method,\C_0)\\
\end{array}$
\end{minipage}
\vline
\hspace{.1in}
\begin{minipage}[b]{0.43\textwidth}
$\begin{array}{l}
\InTextDef{24ex}{\isField(\C\ \m\oR\cR\QM;)}{
\mnot\ \specialName(\m)}\\
\InTextDef{24ex}{\isWith(\C'\ \QM{with#}\m \oR \C\ \x\cR\QM;, \C_0)}{}\\
\hspace{.3in}\C_0 <: \C', \mBody(\m, \C_0) = \C\ \m\oR\cR\QM;
\ \mand\ \mnot\ \specialName(\m)\\
\InTextDef{24ex}{\isSetter(\C'\ \QM_\m \oR \C\ \x\cR\QM;, \C_0)}{}\\
\hspace{.3in}\C_0 <: \C', \mBody(\m, \C_0) = \C\ \m\oR\cR\QM;
\ \mand\ \mnot\ \specialName(\m)\\
\end{array}$
\end{minipage}
\caption{The $\otherMethod$ and $\valid$ functions (left) and auxiliary functions (right).}
\end{figure*}

@@

\begin{figure*}[t]\label{figure:ofmethod}
\centering
\hspace{-.2in}
\begin{minipage}[b]{0.53\textwidth}
$\begin{array}{l}
\InTextDef{5em}{\ofMethod(\C_0)}{
 \QM{static}\ \C_0\ \QM{of} \oR \C_1\ \QM_\m_1\QM,\ldots \C_n\ \QM_\m_n\cR\
\QM{\{}}\\
\tab\QM{return new}\ \C_0 \oR\cR\ \QM{\{}\\
\tab\tab \C_1\ \m_1 = \QM_\m_1\QM;\ldots \C_n\ \m_n = \QM_\m_n\QM; \\
\tab\tab
\C_1\ \m_1\oR\cR\ \QM{\{return }\ \m_1\QM{;\}}\ \ldots
\C_n\ \m_n\oR\cR\ \QM{\{return }\ \m_n\QM{;\}}\\
\tab\tab\withMethod(\C_1,\m_1,\C_0,\es_1)\ldots\withMethod(\C_n,\m_n,\C_0,\es_n)\\
\tab\tab\setterMethod(\C_1,\m_1,\C_0)\ldots\setterMethod(\C_n,\m_n,\C_0)\\
%\tab\tab\cloneMethod(\C_0,\es)\\
%\tab\tab\withMethod(\C_0)\\
\tab\QM{\};\}} \\
\InTextWith{\C_1\ \m_1\QM{();},\ldots \C_n\ \m_n\QM{();} = \fieldsFunc(\C_0)}\\
\hspace{.5in}\mbox{ and }\es_i=\m_1\QM,\ldots\QM, \m_{i-1}\QM,\QM{_val,}\m_{i+1}\QM,\ldots\QM, \m_n
\end{array}$
\end{minipage}
\vline
\hspace{.2in}
\begin{minipage}[b]{0.4\textwidth}
$\begin{array}{l}
\InTextDef{16ex}{\method\in\fieldsFunc(\C_0)}{}\\
\hspace{.3in}\isField(\method)\ \mand\
\method=\mBody(m^\method,\C_0)\\
\InTextDef{10em}{\withMethod(\C,\m,\C_0,\es)}{}\\
\hspace{.2in}\C_0\ \QM{with#}\m\oR \C\ \QM{_val}\cR\ \QM{\{}
\QM{return}\ \C_0\QM{.of(}\es\QM{);\}} \\
\InTextWith{\mBody(\QM{with#}\m,\C_0) \mbox{ having the form }\mh\QM;}\\
\InTextDef{10em}{\withMethod(\C,\m,\C_0,\es)}{\emptyset\mbox{ otherwise}}\\
\InTextDef{10em}{\setterMethod(\C,\m,\C_0)}{}\\
\hspace{.2in}\C_0\ \QM_\m\oR \C\ \QM{_val}\cR\ \QM{\{}
 \m\QM{= _val;return this;\}} \\
\InTextWith{
\mBody(\QM_\m,\C_0) \mbox{ having the form }\mh\QM;}\\
\InTextDef{10em}{\setterMethod(\C,\m,\C_0)}{\emptyset\mbox{ otherwise}}\\
%\cloneMethod:&\cloneMethod(\C_0,\es)=
%\C_0\ \QM{clone()\{return}\ \C_0\QM{.of(}\es\QM{);\}} \\
%&\mbox{iff }
%\mBody(\QM{clone},\C_0) \mbox{ is of form }\mh\QM;\\
%&\cloneMethod(\C_0,\es)=\emptyset\mbox{ otherwise}\\
\end{array}$
\end{minipage}
\caption{The generated $\QM{of}$ method (left) and auxiliary functions (right).}
\end{figure*}

@@

Figure~\ref{figure:translation} presents the translation functions. In the first function, $\mixinAnn$
injects refined methods to interface $\C_0$, while in the second function, $\weakAnn$ invokes
$\ofMethod(\C_0)$ and generates the $\QM{of}$
method for $\C_0$, if such a method does not exist in its domain, and all the abstract methods are
valid for the annotation. Figure~\ref{figure:valid} and Figure~\ref{figure:ofmethod}\haoyuan{Refs are wrong!?} present more details on the auxiliary
functions. The formal definition is available in Appendix~\ref{subsec:translation}.
